A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility

### 2019-05-15 paper.Rmd
reword small parts of challenges

Providing a well documented dataset alongside research requires meeting several challenges. This includes understanding all the pieces and features of documentation such as metadata, licenses, and raw data; where to literally share the data; how to ensure long term provenance of the data.

One challenge is that better documentation requires more time, and that higher impact data needs better documentation.

Sharing data with colleagues: binary data is quick to share, but not as good as something like a simpler format like CSV (ask Laura DeCicco re this)

Providing the right amount of documentation for your data is challenging. Too much is overwhelming; too little and you don't know anything. To illustrate this, imagine two datasets. The first is contained in a folder with dozens of data files and several papers on the topic. The second contains only a single CSV file. The first is too much; understanding it requires a high time cost. The second is too little; we don't know anything about what the data is or why it was collected. The challenge is to provide the right level of detail, somewhere between these two extremes.

@@

There is also a challenge in understanding the impact of data. Data with high potential for impact should be made easier to understand and share. This can be seen in the research created from the 50 hectare plot.

>>>>

Providing a well documented dataset alongside research requires meeting several challenges. This includes understanding all the pieces and features of documentation such as metadata, licenses, and raw data; knowing where to share the data to ensure long term storage.

Better documentation requires more time. Higher impact data needs better documentation.

@@

There is also a challenge in understanding the impact of data. Data with high potential for impact should be made easier to understand and share. This can be seen in the research created from the 50 hectare plot, discussed in section ... - this dataset was challenging to understand without special domain expertise.

Simpler format data like CSV is more reliable than binary serialised/compressed data (ask Laura DeCicco re this).

Providing the right amount of documentation for your data is challenging. Too much is overwhelming; too little and you don't know anything. For example, compare a folder with dozens of data files and several papers, to a single CSV file. The first is too much, and understanding it requires a high time cost. The second is too little; we don't know anything about what the data is or why it was collected. The challenge is to provide the right level of detail, somewhere between these two extremes.
